---
title: "Lab 00 - Hello IDS!"
author: "INSERT YOUR NAME HERE"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Wen", "Santiago", "Jin", 
           "Casper", "Aidan"),
  github_username = c("NovaIMario", "AidanCK", "SantiagosGitHub(unknown)", 
                      "aux1r", "King-141319"), 
  colour = c("Blue", "Red", "Red", 
             "Blue", "Blue"),
  hobby = c("Playing Games", "Football", "Basketball", 
            "Video Games", "Tennis"),
  favourite_number = c(7, 3435, 19, 17, 12)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The graph displays peoples favorite numbers on a bar graph.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Insert text here", 
          y = "Insert text here",
          title = "Insert text here")
```

The labs function changes the labels of the plot.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

A pie chart would be effective at displaying the information, because there may be many small areas.
